\documentclass[10pt]{exam}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage[normalem]{ulem}
\usepackage{stmaryrd}

\usepackage{color}
\usepackage{colortbl}
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepred}{rgb}{0.6,0,0}
\definecolor{deepgreen}{rgb}{0,0.5,0}
\definecolor{gray}{rgb}{0.7,0.7,0.7}

\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = black, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor    = blue  %Colour of citations
}

\usepackage{listings}
\lstset{
    basicstyle={\ttfamily}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand*{\hl}[1]{\colorbox{yellow}{#1}}

\newcommand*{\answerLong}[2]{
    \ifprintanswers{\hl{#1}}
\else{#2}
\fi
}

\newcommand*{\answer}[1]{\answerLong{#1}{~}}

\newcommand*{\TrueFalse}[1]{%
\ifprintanswers
    \ifthenelse{\equal{#1}{T}}{%
        %\hl{\textbf{TRUE}}\hspace*{14pt}False
        \hl{\texttt{True}}\hspace*{20pt}\texttt{False}\hspace*{20pt}\texttt{Open}
    }{
        \ifthenelse{\equal{#1}{F}}{
        %True\hspace*{14pt}\hl{\textbf{FALSE}}
        \texttt{True}\hspace*{20pt}\hl{\texttt{False}}\hspace*{20pt}\texttt{Open}
        }
        {
            \texttt{True}\hspace*{20pt}{\texttt{False}}\hspace*{20pt}\hl{\texttt{Open}}
        }
    }
\else
    \texttt{True}\hspace*{20pt}\texttt{False}\hspace*{20pt}\texttt{Open}
\fi
} 
%% The following code is based on an answer by Gonzalo Medina
%% https://tex.stackexchange.com/a/13106/39194
\newlength\TFlengthA
\newlength\TFlengthB
\settowidth\TFlengthA{\hspace*{1.8in}}
\newcommand\TFQuestion[2]{%
    \setlength\TFlengthB{\linewidth}
    \addtolength\TFlengthB{-\TFlengthA}
    \noindent
    \parbox[t]{\TFlengthA}{\TrueFalse{#1}}\parbox[t]{\TFlengthB}{#2}
    \vspace{0.25in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem{theorem}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{refr}{References}
\newcommand{\E}{\mathbb E}
\newcommand{\R}{\mathbb R}
\DeclareMathOperator{\nnz}{nnz}
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\determinant}{det}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\I}{\mathbf I}
\newcommand{\Q}{\mathbf Q}
\newcommand{\p}{\mathbf P}
\newcommand{\pb}{\bar {\p}}
\newcommand{\pbb}{\bar {\pb}}
\newcommand{\pr}{\bm \pi}

\newcommand{\trans}[1]{{#1}^{T}}
\newcommand{\loss}{\ell}
\newcommand{\w}{\mathbf w}
\newcommand{\x}{\mathbf x}
\newcommand{\y}{\mathbf y}
\newcommand{\lone}[1]{{\lVert {#1} \rVert}_1}
\newcommand{\ltwo}[1]{{\lVert {#1} \rVert}_2}
\newcommand{\lp}[1]{{\lVert {#1} \rVert}_p}
\newcommand{\linf}[1]{{\lVert {#1} \rVert}_\infty}
\newcommand{\lF}[1]{{\lVert {#1} \rVert}_F}

\newcommand{\Ein}{E_{\text{in}}}
\newcommand{\Eout}{E_{\text{out}}}
\newcommand{\Etest}{E_{\text{test}}}
%\newcommand{\I}{\mathbf I}
%\newcommand{\Q}{\mathbf Q}
%\newcommand{\p}{\mathbf P}
%\newcommand{\pb}{\bar {\p}}
%\newcommand{\pbb}{\bar {\pb}}
%\newcommand{\pr}{\bm \pi}
\newcommand{\mH}{m_{\mathcal H}}
\newcommand{\dvc}{{d_{\text{VC}}}}
\newcommand{\HH}[1]{\mathcal H_{\text{#1}}}
\newcommand{\Hbinary}{\HH_{\text{binary}}}
\newcommand{\Haxis}{\HH_{\text{axis}}}
\newcommand{\Hperceptron}{\HH_{\text{perceptron}}}


\newcommand{\ignore}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\printanswers

\begin{document}


\begin{center}
{
\Huge
    More Midterm 3 Practice Problems
}
\end{center}

\begin{problem}
    For each statement below,
    circle \texttt{True} if the statement is known to be true,
    \texttt{False} if the statement is known to be false,
    and \texttt{Open} if the statement is not known to be either true or false.
    Ensure that you pay careful attention to the formal definitions of asymptotic notation in your responses.

\begin{enumerate}
    \item\TFQuestion{F}{If your model is overfitting, then VC theory predicts that you should increase the size of your VC dimension.}
    \item\TFQuestion{T}{If your model is underfitting, VC theory predicts that you should increase the size of your VC dimension.}
    \item\TFQuestion{T}{If you are training a logistic regression model that has low in-sample error $\Ein$ but high generalization error $|\Ein-\Eout|$, then VC theory predicts that increasing the number of data points $N$ in the training set will result in better performance than increasing the number of dimensions $d$.}
    \item\TFQuestion{T}{If you are training a logistic regression model with the polynomial kernel that has high in-sample error $\Ein$ and low generalization error $|\Ein-\Eout|$, then VC theory predicts that increasing the degree of the kernel is more likely to improve performance than decreasing the degree of the kernel.}

    \item\TFQuestion{T}{You have trained a logistic regression model with L2 regularization.  If your training set size $N$ increases, then the optimal soft order constraint regularization hyperparameter $C$ will also increase.}
    \item\TFQuestion{F}{You have trained a logistic regression model with L1 regularization.  If your training set size $N$ increases, then the optimal augmented error regularization hyperparameter $\lambda$ will also increase.}
    \item\TFQuestion{F}{You have trained a logistic regression model with L1 regularization.  If your number of feature dimensions $d$ increases, then the optimal soft order constraint regularization hyperparameter $C$ will also increase.}
    \item\TFQuestion{T}{You have trained a logistic regression model with elastic net regularization.  If your number of feature dimensions $d$ increases, then the optimal augmented error regularization hyperparameter $\lambda$ will also increase.}
    \item\TFQuestion{T}{When training a logistic regression model, if you want the weight vector to be sparse, then you should prefer L1 regularization to L2 regularization.}
    \item\TFQuestion{F}{When training a logistic regression model using L2 regularization, increasing the value of the augmented error regularization hyperparameter $\lambda$ increases the VC dimension.}
    \item\TFQuestion{F}{The elastic net regularization function cannot be applied with the polynomial kernel to a logistic regression model.}

    \item\TFQuestion{T}{You have trained a logistic regression model with the PCA kernel and used a validation set to determine that the optimal output dimension $k$ is 200.  If your training set size $N$ increases, then VC theory predicts that the optimal value for $k$ will increase.}
    \item\TFQuestion{T}{You have trained a MLP with the ReLU activation function and used a validation set to determine that the optimal number of layers is 5 and optimal width is 100.  If your training set size $N$ increases, and you keep the number of layers the same, then VC theory predicts that the optimal width of those layers will increase.}
    \item\TFQuestion{F}{You have trained a boosted decision stump model and used a validation set to determine that the optimal number of base classifiers $T$ is 1000.  If instead of training a decision stump, you train a decision tree of depth 2, then the optimal number of base classifiers will increase.}

    \item\TFQuestion{O}{The VC dimension of neural networks with the ReLU activation function is $\Theta(Ek\log(E))$, where $k$ and $E$ is as-defined in the notes.}
    \item\TFQuestion{T}{The VC dimension of neural networks with the identity activation function is $O(dE)$.}

    \item\TFQuestion{T}{Assume you are training a boosted decision stump model on a dataset with $N=10^6$ and $d=10^6$. Then in the limit as the number of base models $T$ approaches infinity, the training error is guaranteed to approach 0 for all possible datasets.}
    \item\TFQuestion{F}{Assume you are training an SVM with the random features kernel with output dimension $d'$. Then in the limit as $d'$ approaches infinity, the training error is guaranteed to approach 0 for all possible datasets.}

    \item\TFQuestion{T}{In vowpal wabbit, increasing the \lstinline{--bit_precision} hyperparameter increases the model's VC dimension.}
    \item\TFQuestion{F}{In vowpal wabbit, increasing the \lstinline{--hash_seed} hyperparameter increases the model's VC dimension.}
    \item\TFQuestion{F}{In vowpal wabbit, increasing the \lstinline{--ngrams} hyperparameter increases the model's VC dimension.}
    %\item\TFQuestion{F}{In scikit-learn, the \lstinline{sklearn.neighbors.KNeighborsClassifier} with hyperparamater \lstinline{n_neighbors} set to 1 can achieve the Bayes error }
    \item\TFQuestion{F}{In scikit-learn's \lstinline{sklearn.tree.DecisionTreeClassifier} model, increasing the value of the hyperparamater \lstinline{max_depth} increases the VC dimension.}
    \item\TFQuestion{F}{You have trained a scikit-learn \lstinline{sklearn.tree.DecisionTreeClassifier} model, but it is underfitting.  VC theory predicts that increasing the value of \lstinline{min_samples_split} will be more likely to improve performance than decreasing this value.}
    \item\TFQuestion{F}{You are training a scikit-learn \lstinline{sklearn.ensemble.AdaBoostClassifier} model with \lstinline{base_estimator} set to \lstinline{sklearn.tree.DecisionTreeClassifier}.  In order to keep the VC dimension of your model constant, if you increase the value of \lstinline{n_estimators} for the \lstinline{AdaBoostClassifier}, then you should also increase the value of \lstinline{max_depth} for the \lstinline{DecisionTreeClassifier}.}
    \item\TFQuestion{T}{You are training a scikit-learn \lstinline{sklearn.ensemble.AdaBoostClassifier} model with \lstinline{base_estimator} set to \lstinline{sklearn.tree.DecisionTreeClassifier}.  In order to keep the VC dimension of your model constant, if you increase the value of \lstinline{min_samples_split} for the \lstinline{DecisionTreeClassifier} then you should also increase the value of \lstinline{n_estimators} for the \lstinline{AdaBoostClassifier}.}
    \item\TFQuestion{F}{You are using transfer learning to train the final layer of a deep neural network for your specific task.  The \lstinline{ResNet50} model has 50 hidden layers and the \lstinline{ResNet18} model has only 18 hidden layers, and in both cases all layers have the same width.  VC theory predicts that if you use the \lstinline{ResNet50} model you will have a higher generalization error than if you use the \lstinline{ResNet18} model.}
    \item\TFQuestion{F}{You are using transfer learning to train the final layer of a deep neural network for your specific task.  The \lstinline{VGG13} model has 13 hidden layers and the \lstinline{VGG19} model has 19 hidden layers, and in both cases all layers have the same width.  VC theory predicts that if you use the \lstinline{VGG13} model you will have a higher generalization error than if you use the \lstinline{VGG19} model.}
\end{enumerate}
\end{problem}
\end{document}




